% --- Professional experience

\section{Professional experience}

  \cventry
    {Jan. 2019 - Present} % Date(s)
    {Backend Developer} % Job title
    {Mozio Group} % Organization
    {Remote} % Location
    {}
    {
      \begin{itemize} % Description(s) of tasks/responsibilities
        \item {Providing backend solutions and bugfixing mainly with Python, Django and rest-framework over AWS infrastructure.}
      \end{itemize}
    }


  \cventry
    {Jul. 2016 - Jan. 2019} % Date(s)
    {Backend \& Machine Learning Developer} % Job title
    {Machinalis SRL} % Organization
    {Cordoba, Argentina} % Location
    {}
    {
      \begin{itemize} % Description(s) of tasks/responsibilities
        \item {Implemented and deployed a microservice that uses machine learning and predicts payment status for the main ecommerce site in Latin America (Python, Flask, XGBoost, Scikit-Learn, Docker).}
        \item {Implemented RESTful API backend for big data analysis system focusing on high-availability, fault tolerance, and auto-scaling (Python, Django, DRF, Postgres, Docker, Elasticsearch, Jenkins).}
        \item {Implemented microservices that uses machine learning techniques for model sentiment analysis and topic detection for people and social networks analysis (NLP, Clustering, Python, Pandas, Scikit-Learn).}
      \end{itemize}
    }

  \cventry
    {Sep. 2015 - Jul. 2016} % Date(s)
    {Software Engineer} % Job title
    {Taller Technologies} % Organization
    {Cordoba, Argentina} % Location
    {}
    {
      \begin{itemize} % Description(s) of tasks/responsibilities
        \item {Software developer for Windows kernel driver with security purposes (C\#, Intel Performance Monitoring Unit).}
        \item {Embedded software development for an UAV project (C/C++, BeagleBone Black, LPCExpresso, TI's TMS, MBED, RTEMS).}
      \end{itemize}
    }

  \cventry
    {Dec. 2014 - Aug. 2015} % Date(s)
    {Unit Engineer} % Job title
    {VENG S.A. for CONAE} % Organization
    {Cordoba, Argentina} % Location
    {}
    {
      \begin{itemize} % Description(s) of tasks/responsibilities
        \item {Production and test responsible of aerospace equipment for the National Agency of Space Activity.}
      \end{itemize}
    }

  \cventry
    {Aug. 2014 - Dec. 2014} % Date(s)
    {Freelance Software Engineer} % Job title
    {SIANA Systems} % Organization
    {Remote (HQ San Diego, CA)} % Location
    {}
    {
      \begin{itemize} % Description(s) of tasks/responsibilities
        \item {Embedded software developer for home automation appliances (C, C++, Python).}
      \end{itemize}
    }

  \cventry
    {Sep. 2011 - Sep. 2014} % Date(s)
    {Software Engineer} % Job title
    {DTA S.A.} % Organization
    {Cordoba, Argentina} % Location
    {}
    {
      \begin{itemize} % Description(s) of tasks/responsibilities
        \item {Main software developer of an embedded board for the National Agency of Space Activity using NASA and ESA standards (C, 8051 Assembly).}
        \item {Development of desktop applications for ground support equipment for an aerospace satellite (Python, C\#, Labview).}
        \item {Firmware and test software design and development of a general purpose embedded systems development kit based on Freescale Kinetis K60 (C, Freescale Kinetis Assembly, Ethernet standard, I2C, SPI).}
      \end{itemize}
    }

  \cventry
    {Sep. 2007 - Aug. 2011} % Date(s)
    {IT Supporter and Data Networks technician} % Job title
    {Compute Centre of the Exacts, Physic and Natural Sciences School} % Organization
    {Cordoba, Argentina} % Location
    {}
    {
      \begin{itemize} % Description(s) of tasks/responsibilities
        \item {Implementation of a dedicated router for LAN/WAN access providing communication between all school building data network and to the University main network (Debian OS, IPTables, Firewalls, Linux Network).}
        \item {Migration of main building data network to a VPN separated network. Providing privacy between different areas and physical and logical separations inside the building (Debian OS, VPN)}.
        \item {IT support at both buildings of the University}
      \end{itemize}
    }

% --- End of professional experience